### 2023-02-28 doc/src/MSLevel.tex
Upgrade chapter status; remove Duo-PLIC chapter to a separate document
Signed-off-by: John Hauser <31252952+jhauser-us@users.noreply.github.com>

\textbf{%
This chapter is \emph{frozen}, meaning
a functional change is extremely unlikely.
Change will occur only because of some truly critical issue
being identified during public review.%
}
\bigskip

@@

If the system has an original PLIC or \mbox{Duo-PLIC} for backward
compatibility with older software, reset should initialize the
machine-level \z{iprio} array to all zeros.

@@

If the system has an original PLIC or \mbox{Duo-PLIC} for backward
compatibility with older software, reset should initialize the
supervisor-level \z{iprio} array to all zeros.

>>>>

\textbf{%
This chapter is \emph{frozen} and has already passed public review,
making a functional change at this stage extremely unlikely.%
}
\bigskip

@@

If the system has an original PLIC for backward
compatibility with older software, reset should initialize the
machine-level \z{iprio} array to all zeros.

@@

If the system has an original PLIC for backward
compatibility with older software, reset should initialize the
supervisor-level \z{iprio} array to all zeros.
